HBCC - DLPFC - FEATURECOUNTS - GRCh38 - CQN

### 2020-05-19 individual-cohorts/HBCC_DLPFC_FEATURECOUNTS_GRCh38_CQN.Rmd
point counts to data freeze

## Download reprocessed counts (DLPFC)
counts = 'syn21754352'
ALL_USED_IDs[length(ALL_USED_IDs)+1] = counts
COUNT = downloadFile(counts) %>% data.frame()
COUNT$Chr <- NULL
COUNT$Start <- NULL
COUNT$End <- NULL
COUNT$Strand <- NULL

>>>>

## Download reprocessed counts (DLPFC)
counts = 'syn21886235'
ALL_USED_IDs[length(ALL_USED_IDs)+1] = counts
COUNT = downloadFile(counts) %>% data.frame()
COUNT$Chr <- NULL
COUNT$Start <- NULL
COUNT$End <- NULL
COUNT$Strand <- NULL
